---
title: "STAC33 Assignment 8"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

### Can We Predict Men's Height By Looking At Their Feet?
\

Here is the package I will be using in this assignment.  
```{r, message = FALSE}
library(tidyverse)
```
\

**a) Reading and Displaying Data File **

Since I am given _csv_ file, I used the function read_csv().  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `hf` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/heightfoot.csv"
hf <- read_csv(url)
hf
```
There are 33 rows and 2 columns.  
In other words, there are 33 observations of males' height and foot length.  
\

**b) Foot Length vs. Height Scatter Plot**

There are two quantitative variables in `hf`, hence I will be plotting in scatter plot.  
As usual, I use ggplot() to plot the given data frame.  
The _height_ is the output, and the _foot_ is the input.  
I added a trend line, and did not assume linear.  
```{r}
ggplot(hf, aes(y = height, x = foot)) + geom_point() + 
  geom_smooth(se = FALSE)
```
There seems to be a weak-moderate, upward, apparently linear trend.  
I said weak to moderate because about half of the points are not close to the trend.  
That means, men with bigger feet tend to be taller than the men with small feet.  
\

**c) Unusual Observations**

There exists a little “wiggle” in the middle: it goes down briefly and goes back up.  
There is also an outlier that is bothersome.  
Some of the points seems to be little too low but the outlier is the biggest concern.  
\

**d) Regression Model, Residual Plot, and Normal Quantile Plot**

Since I have observed _somewhat_ linear trend, I will fit a straight line.  
```{r}
height.1 <- lm(height ~ foot, data = hf)
summary(height.1)
```
The R-squared is approximately 0.32 or 32%.  
This indicates that the relationship between the two variables is very weak.  
I have said that there seems to be a 'weak-moderate' relationship.  
Hence, I expect the R-squared to be little higher.  
I believe that the outlier has brought the R-squared value down.  
\

Here is the plot of residuals against fitted values.  
```{r}
ggplot(height.1, aes(x = .fitted, y = .resid)) + geom_point()
```
As I mentioned earlier, there is an outlier.  
Hence, I can't really fit a straight line quiet yet.  
\

Finally, here is the normal quantile plot of the residuals in the previous part.  
```{r}
ggplot(height.1, aes(sample = .resid)) + stat_qq() + stat_qq_line()
```
Most of the points seems to be normal along the line except for the outlier.  
\

**e) Behaviour of Unusual Observations in Plot**

As expected, the outlier is far off the trend.  
I have also mentioned that there were points which were too low previously.  
However, in the residual plots and normal quantile plots, it does not seem too problematic.  
\

**f) Creating and Saving New Data Frame**

Observing the original data frame `hf`, I have noticed that the outlier is in row 28.  
Hence, I removed that row from the data frame and saved it as new data frame `hf_new`.  
```{r}
hf_new <- heightfoot[-c(28),]
hf_new
```
There are now 32 observations of males' height and foot length.  
\

**g) Regression Model, Residual Plot, and Normal Quantile Plot for New Data**

Before doing the regression analysis, I just want to see the plot.  
This part is same as the step b), just with different data input.  
```{r}
ggplot(hf_new, aes(y = height, x = foot)) + 
  geom_point() + geom_smooth(se = FALSE)
```
The data is seems more linear now.  
\

I will be fitting a straight line one more time.  
```{r}
height.2 <- lm(height ~ foot, data = hf_new)
summary(height.2)
```
The R-squared is now 0.57 or 57%.  
This is much better than before.  
I can't say that this is good enough.  
However, it is enough to say that there is a moderate relationship.  
\

Here is the plot of residuals against fitted values of the new data frame.  
```{r}
ggplot(height.2, aes(x = .fitted, y = .resid)) + geom_point()
```
This plot looks like a completely random scatter of points.  
Thus, I am completely happy with the straight-line regression that I fitted.  
I see no need to improve it further.  
\

Here is the normal quantile plot of the new data frame.  
```{r}
ggplot(height.2, aes(sample = .resid)) + stat_qq() + stat_qq_line()
```
\

**h) Problems With Plot of New Data Frame**  
There is a little problem with the normal quantile plot.  
The low points are too low and high points are little high.  
Hence, the distribution is not _too_ normal.  
\

**i) Scatter Plot with Two Regression Lines**  

I have first saved the plot of the original plot into a variable.  
I have also assigned its name for the legend.  
Next, I add the plot of the new data frame with its own name for the legend.  
Using manual function, I have added the legend with corresponding colors.  
I have also modified the fill color so that way it is easier to see the difference.  
I saved it into a variable again and displayed it below.  
```{r}
reg1 <- ggplot(hf, aes(y = height, x = foot)) + 
  geom_point() + geom_smooth(aes(color = "With Outlier", fill = "With Outlier"))
reg2 <- reg1 + geom_point(data = hf_new, aes(foot, height)) + 
  geom_smooth(data = hf_new, aes(color = "Without Outlier", 
                                 fill = "Without Outlier"), size = 1) +
  scale_color_manual(name = "Legend", values = c("blue", "red")) +
  scale_fill_manual(name = "Legend", values = c("lightsteelblue", "pink"))
reg2
```
\

**j) Expectation and The Result**  
I have expected that removing the outlier will somewhat resolve the issue.  
Although the result wasn't too dramatic, regression line changed.  
The little "wiggle" smoothed out and the line became more linear.  
Without the outlier, there exists some positive relationship between men's height foot length.  
\
\

**Reference**  

Cameron, A. (2020, October 14). "Mixed fill color in ggplot2 legend using geom_smooth() in r". Retrieved March 25, 2021, from https://stackoverflow.com/questions/64359233/mixed-fill-color-in-ggplot2-legend-using-geom-smooth-in-r