---
title: "STAC33 Assignment 9"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

### 1. Before and After Pulse Rate on Different Sex
\

Here are the packages I will be using in this assignment.  
```{r, message = FALSE}
library(tidyverse)
library(broom)
```
\

**a) Reading and Displaying Data**  

Since I am given _csv_ file, I used the function read_csv().  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `pulse` is created and displayed below. 
```{r}
url <- "http://ritsokiguess.site/STAC32/pulsemarch.csv"
pulse <- read_csv(url)
pulse
```
There are 40 rows and 3 columns.  
\

**b) Scatterplot With Regression Lines**  

There are two quantitative and one categorical variables I have to account for.  
Hence, I used the scatterplot distinguished by color.  
I used the "lm" method for a simple linear regression model.  
I added a title, which is defined before ggplot.  
```{r}
t1 = "After-March Pulse Rate Against Resting Pulse Rate for Males and Females"
ggplot(pulse, aes(x = Before, y = After, colour = Sex)) +
  geom_point() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle(t1)
```
\

**c) Any Effects Showing Up On Plot?**  

Generally, the plot tells you that with higher _before_ pulse rate, the _after_ pulse rate is higher.  
There exists a slight difference between females' and males' average trend.  
The males seems to have somewhat lower average pulse rate compared to females but the degree of consistency is low.  
There is an upward, moderate, linear trend.  
I said the relationship is not strong because many points are away from the line.  
\

**d) Regression Predicting After Pulse Against Other Two Variables**  

I have observed a linear trend, hence I will fit a linear model.  
```{r}
pulse.1 <- lm(After ~ Sex + Before, data = pulse)
summary(pulse.1)
```

```{r}
tidy(pulse.1)
```
Slope for _Before_ says that if resting pulse rate is 1 higher, then the after pulse rate will be increased by 0.91 after marching.  
The P-value attached to SexMale is 0.038, which is less than 0.05.  
This means that when you know the resting pulse rate, there will be a difference between males and females.  
The R-squared for this regression is about 65%, which is not so good.  
This means if you know both before pulse rate and sex, you can somewhat predict the pulse rate after marching.  
\

**e) Any Surprises?**  

I decided that the trend was “moderate” in strength earlier.
I am less surprised because I have already expected slight significance.  
The P-value indicated that the slope is actually significantly different from zero.  
Since there were only 40 observations, I was able to get a significant slope.  
\

**f) Estimate for Sex**  

Since sex is categorical, lm uses the first category, Female, as the baseline.  
In the regression output, the slope for sex is about -4.8, labelled _SexMale_.  
This means that at any given resting pulse rate, the mean pulse rate for males after marching is about 4.8 less than for females.  
This is pretty much what I have observed in the my graph.  
\

### 2. Coefficient of Variation of a Vector
\

**a) Writing Function to Calculate CV**  

I have a header line with function name called _cv_ and input value _x_.  
Inside the body, it calculates the standard deviation of x divided by the mean
of x to output/return.  
I have set na.rm to true to remove any missing values before calculating the sd and mean.  
```{r}
cv <- function(x) {
  sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
}
```
\

**b) CV of The Set of Integers 1 through 5**  

I define a vector from integers 1 through 5 in `d`.  
Then, I pass that vector to the function I made in the previous part.  
```{r}
d <- c(1:5)
cv(d)
```
The coefficient of variation of integers 1 through 5 is 0.53.  
\

**c) What Happens With Negative Entries?**  

```{r}
v <- c(-2.8, -1.8, -0.8, 1.2, 4.2)
cv(v)
```
According to the function I made, the coefficient of variation is extremely large.  
This doesn't make sense because the CV is interpreted in percentages.  
This is because when I add all the values, the sum is equal to zero.  
\

**d) Revised CV Function**  

I set error to true as stated in the question first.  
Then, I add extra condition to the previous _cv_ function I made.  
I check if the given parameter is positive, if not, function is not executed.  
```{r, error = TRUE}
cv <- function(x) {
  stopifnot(x < 0)
  sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
}
cv(v)
```
Checked with _v_ which has negative entries, and it successfully displays an error.  
\

