---
title: "STAC33 Assignment 4"
output:
  pdf_document: default
  html_notebook: default
---
\

I will be using the packages called `tidyverse`, and `smmr`.  
```{r, message=FALSE}
library(tidyverse)
library(smmr)
```
\

### 1. Going to Dentist is Scary

**a) Reading in Data and Displaying**  
The given data set is a csv file, so I use the read_csv function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data set `bp` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/blood_pressure1.csv"
bp <- read_csv(url)
bp
```
There are 10 rows and 3 columns.  
\

**b) What Kind of Design is This?**  
This is a "matched-pairs" design.  
Each randomly-chosen individuals in this experiment have their blood pressure measured before the appointment.  
Then, their blood pressure is measured again one hour after their appointment is finished.  
Since I have two different measurements for each individuals, the matched-pair analysis is more suitable.  
\

**c) Running Suitable _t_-Test**  
The experiment is trying to prove that people might have higher blood pressure on average before the dentist appointment and an hour after.  
I need to use a one-sided alternative.  
```{r}
with(bp, t.test(before, after, alternative = "greater", paired = T))
```
The p-value from the preceding result is 0.0075 which is a whole lot less than 0.05.  
Hence, here is no doubt at all that people's blood pressure is higher **before** the appointment in the waiting room.  
This also supports my intuition - I expected something like this, because almost everyone's blood pressure appears to be greater before than after.  
\

**d) Running Matched-Pair Sign Test**  
I will need the difference between the values of before and after for both the sign test and the normal quantile plot.  
So, I should calculate and save them first.  
```{r}
bp %>% mutate(diff = before - after) -> bp_diff
```
\

Then, I perform a matched pair sign test.  
```{r}
sign_test(bp_diff, diff, 0)
```
Since we are trying to prove that the blood pressure is _higher_, I need to take the _upper_ p-value.  
The sign test gives upper p-value of 0.055 which is slightly greater than 0.05, hence we fail to reject the null hypothesis.  
However, this contradicts the conclusion I drew from the _t_-test.  
From this, I can conclude two things.  
The matched pairs analyses assume (theoretically) that differences are normally distributed.  
Since the two results failed to give same result, this could be an evidence that the distribution of the data is not normal.  
Also, notice that there are only 10 observations in the data.  
This is not large enough to get any substantial help from the Central Limit Theorem, hence _t_-test may not have been appropriate for this.  
\

**e) Drawing a Normal Quantile Plot**  
```{r}
ggplot(bp_diff, aes(sample = diff)) + stat_qq() + stat_qq_line()
```
Evidently, there are many outliers.  
The lowest value is too low and the highest value is too high, which tells me that this is a long-tailed distribution.  
Also, With only 10 observations as I have here, the _t_-test would be very problematic.  
\

**f) Conclusion**  
In all, the matched-pair sign test was more suitable to run for this data.  
There were three factors that showed the _t_-test is rather not advisable.  
The distribution was non-normal, long-tailed, and the given data had small sample size.  
Hence, it would be more wise to use the sign test to get the appropriate result.  
\

### 2. Men Handspans vs. Women Handspans  

**a) Reading in Data and Displaying**  
The given data set is a text file.  
When I open the file, the values are separated by a space, so I use the read_delim function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data set `hand` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/handspan.txt"
hand <- read_delim(url, " ")
hand
```
There are 190 rows and 2 columns.  
\

**b) Facetted Normal Quantile Plot**  
Before facetting, I want to see the whole picture.  
```{r}
ggplot(hand, aes(sample = handspan)) + stat_qq() + stat_qq_line()
```
I can observe from the graph that the distribution has some outliers with low point being too low.  
\

Now, I want to see whether male students have a larger mean handspan than female students by facetting.  
F stands for "females" and M stands for "males".  
```{r}
ggplot(hand, aes(sample = handspan)) + stat_qq() + stat_qq_line() + 
  facet_wrap(~sex)
```
From this, I can definitely see that both groups have outliers.  
\

**c) MMT or _t_-Test?**  
I noticed non-normality in both groups.   
Both have outliers at the low end that would be expected to pull the mean downward.  
The values are also very bunched up and not spread out.  
I may also believe that the "female" group distribution could be skewed to the left, but I do not see too much clusters in the high end but rather very clustered in the middle.  
In turn, I should use the Mood's median test to compare the handspans of men and women.  
\

**c) Mood's Median Test**  
If I just run the Mood's median test from the `smmr` package, I get the following:  
```{r}
median_test(hand, handspan, sex)
```
The p-value is extremely small, hence we fail to reject the null.  
In fact, there is a substantial difference in median for females and males.  
\

I noticed that there are only $17 + 82 + 65 + 11 = 175$ observations in the table, but there are 190 observations in the `hand` dataset.  
This is means that 15 of the observations were equal to the overall median, and had to be thrown away.  
\

Some extra steps and codes from here:  
To avoid this issue, I am going find out how many individuals in each groups had equivalent value of handspan as the median.  
```{r}
hand %>% summarize(med = median(handspan))
```
The median is 21.5 which would have issues with values-equal-to-median since some of the values in `hand` have same value.  
\

```{r}
hand %>% filter(handspan == 21.5)
```
I found that there are 4 females and 11 males with 21.5 handspan.  
I should account for this for more accurate result.  
\

```{r}
(hand %>% summarize(med = median(handspan)) %>% pull(med) -> m)
tab = with(hand, table(sex, handspan > m))
tab
```
Since this methods account for the missing values, I should use this table for Mood's median test.  
\

```{r}
chisq.test(tab, correct = FALSE)
```
Either way, the Mood's median test gives me a very small P-value which tells me that the groups do not all have the same median.  
In conclusion, the males have longer handspans than females.  