---
title: "STAC33 Assignment 5"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

### Introduction  

There are countlessly many shampoos that are advertised as effective in treating dandruff on the market. Consumers are often misled by the facts and statistics displayed in the advertisement, **_"100% Dandruff-Free!"_** for example. The question is, are all dandruff shampoos effective? This study is designed to analyze four different types of shampoos that are meant to be effective for controlling dandruff flaking and distinguish their effects on subjects to find the best one of the four -- the _PyrI_, _PyrII_, _Keto_, and the _Placebo_. This study is carried out on subjects who were randomly assigned to a shampoo, and were measured the amount of flaking on a scale of 0-10 (less being better), after six weeks of treatment. The final flaking score is the sum of flaking in eight sections of scalp of each subjects. We compare the mean flaking score for each shampoos.    
\

### Processing Data   

We need to read in the data first.  
This is the package needed.  
```{r, message = FALSE}
library(tidyverse)
```
\

Since the given data values are separated with tabs, we use read_delim function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `flake` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/dandruff.txt"
flake <- read_delim(url, "\t")
flake
```
There are 355 rows and 4 columns.  
\

### Analysis   

We first begin by observing the boxplot of each treatment.  
```{r}
flake %>% 
  mutate(Treatment = fct_inorder(Treatment)) %>% 
  ggplot(aes(x = Treatment, y = Flaking)) + geom_boxplot()
```
It looks like the median is lowest for _Keto_ shampoo and highest for _Placebo_ shampoo.  
The _PyrI_ shampoo has few outliers and the median is equivalent to the first quartile.    
Given large samples, the spreads are unequal.  
\

We should see if the distribution for each shampoo is normal to proceed with variance test.  
```{r}
ggplot(flake, aes(sample = Flaking)) + stat_qq() + stat_qq_line() + 
  facet_wrap( ~ Treatment)
```
Although we expected outliers, the points are close along the line.  
The four shampoos have normal distributions.  
\

All samples are normal enough.  
However, the spreads are not equal, especially because _Placebo_ is more spread out.  
We use the Welch-ANOVA test which seems to be the best appropriate choice.  
```{r}
oneway.test(Flaking ~ Treatment, data = flake)
```
The p-value is extremely small, hence we reject our null hypothesis.  
This indicates that the flaking score for each shampoos are not equivalent.  
\

This is another package that is needed to perform the Games Howell Test.  
We perform this test for detailed information to see which ones are different from which.  
```{r, message = FALSE}
library(PMCMRplus)
```

```{r}
gamesHowellTest(Flaking ~ factor(Treatment), data = flake)
```
Here, we see that with _PyrI_ and _PyrII_ shampoos, there aren't any significant difference on their effectiveness.  
However, other comparisons show huge differences.  
\

This is not enough to figure out which shampoo is the best choice.  
We now need to find the mean values for each shampoo and see which one is the lowest since lower the flaking, the better.  
```{r}
flake %>%
  group_by(Treatment) %>%
  summarize(mean = mean(Flaking))
```
The _Keto_ shampoo has lowest mean value, meaning lowest flaking score.   
As the Games Howell Test testified, the _PyrI_ and _PyrII_ has almost no difference.  
The _Placebo_ shampoo has the higest mean value.  
\

### Conclusion   

From this study, we found that there were significant difference in the effectiveness of the dandruff shampoos. Both _Keto_ and _Placebo_ shampoos compared with other shampoos showed great differences, but _PyrI_ and _PyrII_ didn't show great difference. Comparing the mean, we found that the _Keto_ shampoo is the best dandruff shampoo of the four. From most effective to least effective order, _Keto_, _PyrII_, _PyrI_, and _Placebo_. If one is looking for a dandruff shampoo to use, he or she should look for **Keto** shampoo and avoid _Placebo_ shampoo. This is a generalized conclusion. However, the result could have been different if the treatment lasted longer than six weeks. To my knowledge, skincare products or other medical remedies usually need longer time for the effect to take place. 
