---
title: "STAC33 Assignment 10"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

These are the packages I need for this assignment.  
```{r, messsage = FALSE, error = FALSE}
library(tidyverse)
library(lubridate)
```
\

### 1. A Student's Sleep Time  
\

**a) Reading and Displaying Data File**  
Since the given file is in .csv format, I use the read_csv function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `sleep` is created and displayed below.  

```{r}
my_url <- "http://ritsokiguess.site/STAC33/sleeping.csv"
sleep <- read_csv(my_url)
sleep
```
There are seven rows and three columns.  
The _bed.time_ and _rise.time_ are both _POSIXct_ data type which stores dates and times.  
The _sleep.time_ hold numeric values with decimal points (dbl means double).  
\

**b) Number of Hours Student Was In Bed**  

First, I am going to create another column that contains the time student was in bed.  
Then, I change that data type into numerical values and save it in another column.  
The mutated dataframe `sleep` is displayed below.  
```{r}
sleep %>% mutate(
  in.bed = (rise.time - bed.time),
  in.bed.hours = as.numeric(in.bed)
  ) -> sleep
sleep
```
There are seven rows and five columns.  
There are two new columns that contain fractional number of hours that the student was in bed.  
THe _in.bed_ column contains time data type, and _in.bed.hours_ contains numerical value.  
\

**c) Sleep Efficiency of Each Night**  

I decided to label each night as numbers first.  
Then, I calculated sleep efficiency by dividing the sleep time by time in bed.  
I stored those values in a new column and mutated to `sleep` data frame.  
I have displayed the nights with sleep efficiency and arranged in descending order.  
```{r}
sleep %>% mutate(
  night = (1:7),
  sleep.efc = sleep.time / in.bed.hours
) -> sleep
sleep %>% select(night, sleep.efc) %>% arrange(desc(sleep.efc))
```
There are seven rows and two columns.  
I can conclude that on the 7th night, the sleep efficiency was the highest.  
The highest sleep efficiency was about 93.73%.  
\

**d) Displaying Time Spent In Bed**  

I selected the columns I need which is _in.bed_ and _in.bed.hours_ column from `sleep`.  
Then, using mutate(), I have calculated the time in bed in minutes and seconds.  
I have stored them in each columns and they are displayed below.  
```{r}
sleep %>% select(in.bed, in.bed.hours) %>%
  mutate(
    in.bed.minutes = (in.bed / dminutes(1)),
    in.bed.seconds = (in.bed / dseconds(1))
    )
```
There are seven rows and four columns.  
I can see the time in bed in hours, minutes, and seconds.  
\

**e) Graphing Time Went To Bed**

I decided to plot it as a scatterplot with lines.  
I have observed that the time that this student goes to bed fluctuates time to time.  
```{r}
# select the columns I need, and save to new data frame
sleep %>% select(bed.time, night) -> bedtime
# extract hours, minutes, seconds, and convert all to seconds
bedtime %>% mutate(
  hour = abs(hour(bed.time) - 12),
  minute = minute(bed.time),
  second = second(bed.time),
  time = second + (minute*60) + hour*60*60) -> bedtime
# adding title to the graph
t1 = "Time Went to Bed On Each Night"
# plotting scatterplot
ggplot(bedtime, aes(x = night, y = time)) + geom_point() + geom_line() +
  ggtitle(t1)
```
\

### 2. The Least Squares Estimates  
\

**a) Reading and Displaying Data File**  

Since the given file is in .csv format, I use the read_csv function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `sleep` is created and displayed below.  

```{r}
my_url <- "http://ritsokiguess.site/STAC32/heightfoot.csv"
hf <- read_csv(my_url)
hf
```
There are 33 rows and 2 columns.  
\

**b) Calculating The Least Squares Estimates**  

I have wrote comments within the code for easier understanding.  
I have calculated transpose of X prior to complicated calculation.  
```{r}
# X with column with 1s and columns with explanatory variable
X <- cbind(1, hf$foot)
# response variable vector
y <- hf$height
# transpose of X
Xt <- t(X)
# calculating least square estimates
lse <- solve(Xt %*% X) %*% Xt %*% y
# output
lse
```
The output shows that the intercept is at 34.3363 and the slope is 1.3591.  
\

**c) Comparing With Regression Analysis**  

The explanatory variable is _height_ and the response variable is _foot_.  
Hence, I run a height ~ foot linear regression, with the data frame `hf`.  
The summary of the regression is displayed below.  

```{r}
height.1 <- lm(height ~ foot, data = hf)
summary(height.1)
```
The intercept is 34.3363 and the slope is 1.3591.  
This matches the least squares estimates I've calculated, hence, my calculation is verified.  
\
