---
title: "STAC33 Assignment 2"
output: html_notebook
---
\

I will be using the package called `tidyverse`.
```{r, message=FALSE}
library(tidyverse)
```
\

### 1. Cholesterol Measurements  

**a) Reading in Data and Displaying**  
The given data set is a csv file, so I use the read_csv function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data set `cholest` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/cholest.csv"
cholest <- read_csv(url)
cholest
```
This table has 30 rows and 4 columns.  
\

**b) Histogram: Cholesterol Levels of Controlled Patients**  
Since there is one quantitative variable I will be dealing with, which is the _control_ column, I use the histogram to plot the data.  
From PAISIS Chapter 5, I learned how to choose the appropriate number of bins to use.  
Since the data set `cholest` has 30 rows, the sample size is 30. I find the next power of 2 above that, which is $2^5 = 32$.  
Then, I take the exponent and add 1 to arrive at getting 6 bins.  
```{r}
ggplot(cholest, aes(x = control)) + geom_histogram(bins = 6)
```
Observing the histogram, it is clear that the distribution is skewed to the right.  
\

**c) Hypothesis Testing and P-Value**  
I will be using one-sample t-test to find whether such evidence exists.  
Let $\mu$ represent the population mean, or in other words, the mean cholesterol level of the control patients.  
The null hypothesis is $H_0 : \mu = 200$, that the mean is equal to 200, and the alternative is $H_a : \mu < 200$, that the mean is less than 200.  
```{r}
t.test(cholest$control, mu = 200, alternative = "less")
```
The p-value is actually greater than our $\alpha = 0.05$, hence I cannot reject the null hypothesis.  
I can conclude that there is **no** evidence that the mean cholesterol level of the control patients is less than 200.  
\

**d) Confidence Interval**  
The values that population mean cholesterol levels can take can be found by getting the confidence interval.  
```{r}
with(cholest, t.test(control))
```
The result shows that the population mean cholesterol level is from 184.8 to 201.5 with 95% confidence.  
\

**e) Observation**   
The boxplot I created earlier shows that the distribution is skewed to the right, which indicates that I should doubt my t-test. However, the sample size is 30. The Central Limit Theorem suggests that the sample size is large enough to overcome the skewness. Hence, I am reasonably happy to trust the t-test I performed.  

### 2. Anchoring Effect  

**a) Reading in Data and Displaying**  
The given data set is a csv file, so I use the read_csv function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data set `anchoring` is created and displayed below.
```{r}
url <- "http://ritsokiguess.site/STAC32/anchoring.csv"
anchoring <- read_csv(url)
anchoring
```
There are 21 rows and 2 columns.  
\

**b) Boxplot: US vs. Australia**  
There is one quantitative variable and one categorical variable, hence I used the boxplot to graph the data set `anchoring`.
```{r}
ggplot(anchoring, aes(x = anchor, y = estimate)) + geom_boxplot()
```

**c) Why Welch _t_-test?**  
Generally speaking, the two tests are very similar, and is fine to use either one.  
However, when the groups from the data set have very different SDs, the pooled _t_-test can go wrong.  
Hence, in most cases, it is better to use the Welch _t_-test because it works when the population from the sample have different SDs and also works when those SDs are the same.  
\

**d) Welch-Satterthwaite Test**  

```{r}
t.test(estimate ~ anchor, data = anchoring, alternative = "less")
```
The mean for students who were told about _australia_ is 22.5 and the mean for for students who were told about _US_ is 88.35.  
\

**e) Conclusion**  
From the Welch Two Sample _t_-test, the p-value came out to be 0.006019 which is way smaller than the $\alpha = 0.05$.  
Hence, the null hypothesis is rejected.  
In conclusion, the test shows that there **is** indeed an evidence that the anchoring effect exists. This means that the assumption that the guesses for the students given the US as an anchor will be higher than for the students given Australia as an anchor is true.  
