---
title: "STAC33 Assignment 7"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

### New York City Flights
\

I will be using packages called `tidyverse` and `nycflights13`.
```{r, message = FALSE}
library(tidyverse)
library(nycflights13)
```
\

**a) Three Major NYC Airports**

Let's take a look at the data frame `airports` first.  
```{r}
airports
```
It contains 1458 rows and 8 columns.  
Notice that there is _faa_ column that contains airport codes and _name_ column that contains airport names.  
\

I am given that the three major airports have the codes, EWR, JFK, LGA.  
I use the filter() function to pick out the rows with corresponding airport codes from `airports`.  
Then, I select the _faa_ and _name_ columns which are the only necessary information.  
```{r}
airports %>% filter(faa == "EWR" | faa == "JFK" | 
                      faa == "LGA") %>% select(faa, name)
```
Hence, the names of the three major NYC airports are Newark Liberty Intl, John F Kennedy Intl, and La Guardia.  
\

**b) Number of Flights From Three Major Airports**

Take a look at the data frame `flights`.  
```{r}
flights
```
There are 336776 rows and 19 columns.  
\

Since I am not sure if the data frame contains only the three major airports, I use the filter() function.  
Then, I save it to a new variable called `major`.  
```{r}
flights %>% filter(origin == "EWR" | origin == "JFK" | 
                      origin == "LGA") -> major
major
```
Note:  
Turns out, the `flights` only contains the required airports.  
\

I count the number of flights from each airports (origin).  
```{r}
major %>% count(origin)
```
There were 120835 flights that departed from EWR airport.  
There were 111279 flights that departed from JFK airport, and 104662 flights that departed from LGA airport.  
\

**c) Top Five Common Destination Airports**

The question asks to display the names of the five most common destination airports for flights, along with the number of flights.  
First, I take the data frame `flights` and count the number of flights for each destinations.  
Then, I slice the first five rows, where the data is arranged from greatest to least number of flights.  
Next, I join such data with the names of each destination from the data frame `airport` that matches with the airport code.  
I only selected the first three columns which are necessary.  
```{r}
flights %>% count(dest) %>%
  slice_max(order_by = n, n = 5) %>% 
  left_join(airports, by = c("dest" = "faa")) %>%
  select(1:3)
```
The top five common destination airports are:  

  1. Chicago Ohare Intl (ORD)
  2. Hartsfield Jackson Atlanta Intl (ATL)
  3. Los Angeles Intl (LAX)
  4. General Edward Lawrence Logan Intl (BOS)
  5. Orlando Intl (MCO)
\
\

**d) Creating New Data Frame for Flights**

First, I must filter out any rows with missing dep_delay values.  
Then, I arrange the data frame in alphabetical order of the origin for a better view.  
I used the inner_join() function because I only want rows with matching time_hour and origin values between `weather` and the `flights`.  
Finally, I select the columns I want to see, which are _origin_, _flight_, _dep_delay_, _time_hour_, and _visib_.  
I crated a new data frame called `FlightsWeather` that contains its departure delay, and the number of miles of visibility for each flight.   
```{r}
flights %>% 
  filter(!is.na(dep_delay)) %>%
  arrange(origin) %>%
  inner_join(weather, by = c("time_hour" = "time_hour",
                             "origin" = "origin")) %>% 
  select(origin, flight, dep_delay, time_hour, visib) -> FlightsWeather
```
\

The data frame `FlightsWeather` is displayed below.  
```{r}
FlightsWeather
```
There are 326993 rows with five columns of my choice.  
\

**e) Visibility vs. Departure Delay**

I will be using the scatterplot since I have two quantitative variables that I need to compare.  
I am comparing the number of miles of visibility to its departure delay.  
Since I am using a large sample, overplotting is expected.  
Hence, I changed the transparency using the _alpha_ parameter and added color to each origin groups.  
```{r}
ggplot(FlightsWeather, aes(x = visib, y = dep_delay)) + 
  geom_point(alpha = 0.1, aes(color = origin)) + 
  geom_smooth(method = "lm")
```
It is very hard to see the general trend with big range of y-axis.  
\

I decided to ignore some of the outliers on the very top and shrink the y-axis so that the points are more spread out.  
The code remains the same, except for the 'ylim()' function to change the axis range.  
```{r}
ggplot(FlightsWeather, aes(x = visib, y = dep_delay)) + 
  geom_point(alpha = 0.1, aes(color = origin)) + 
  geom_smooth(method = "lm") + ylim(0, 600)
```
Although, it is still hard see, I can somewhat observe that the line is going downwards.  
\

Let's take a look at each origin groups.  
```{r}
ggplot(FlightsWeather, aes(x = visib, y = dep_delay)) + 
  geom_point(alpha = 0.1) + facet_wrap(~ origin, scales = "free") +
  geom_smooth(method = "lm")
```
Very hard to see, but each origin groups have downward line of best fit.  
\

Generally, I can say that there is slightly more delay when the visibility is lower due to weather.  
Other way around, there is slightly less delay when the visibility is higher.  
However, the relationship is very weak.  
Hence, the number of miles of visibility and the departure delay has a very weak negative correlation.  
But, as we observed in previous graphs, there are many outliers and points are all over the place.  
For example, sometimes, there is more departure delay even when the visibility is high.  
Therefore, I must say that the departure delay has multiple factors to it, including the number of miles of visibility.  