---
title: "STAC33 Assignment 6"
author: Hyebeen Jung, 1004346512
output: html_notebook
---
\

### Plant Kudzu, Is It Beneficial for Bones?

**a) Observing the Data File**

The data file has two types of columns: treatment and bone_mineral_density.  
There are control, low_dose, and high_dose rows with multiple values of bone density of rats measured in milligrams per square aligned tibble-like.  
Also, the treatment group names are only recorded when it changes.  
The problem I have with this data file is that the columns, under column name bone_mineral_density, have multiple numbers separated by a space and wrapped like a table when a table cell can only contain single value.  
\

**b) Tidying and Displaying the Data**

This is the package I need for this assignment.  
```{r, message = FALSE}
library(tidyverse)
```
\

As suggested in the assignment, I use the read_table function.  
I defined the link into a variable first, rather than reading in directly from the URL.  
The data `kudzu` is created and displayed below.  
```{r}
url <- "http://ritsokiguess.site/STAC32/isoflavones.txt"
kudzu <- read_table(url)
kudzu
```
Notice that the data is very odd and messy.  
I must perform few functions to tidy the data.  
I have decided to keep the headers in this assignment.  
\

First, I use the separate_rows function to separates the values and place each one in its own row.  
The separator for delimiting the collapsed values is a space in this case.  
After this step, there will be some cells with empty values.  
I use the na_if function with empty string ("") as the parameter to replace all empty cells with _NA_.  
Finally, I must fill in missing data from top to bottom using the fill function with the column name parameter.  
I save the modified version to a new dataframe and call it `tidy_kudzu`.  
```{r}
separate_rows(kudzu, bone_mineral_density, sep = " ") %>%
  na_if("") %>% fill(treatment) -> tidy_kudzu
```
\

Here is how the data is sorted out.  
```{r}
tidy_kudzu
```
There are now 45 rows, 15 each per treatment group, with 2 columns, as required.  
\

However, notice that the bone_mineral_density column stores character values.  
Hence, I must also convert this into numerical form so that the dataframe is suitable for making graphs.  
I use the as.numeric function to convert only the second column of `tidy_kudzu` dataframe.  
```{r}
tidy_kudzu$bone_mineral_density <- as.numeric(tidy_kudzu$bone_mineral_density)
tidy_kudzu
```
Notice that the second column has been successfully modified to a numerical column.  
\

**c) Plotting Data**

Let's see if ANOVA test is suitable to compare the bone mineral density for different treatments.  
I first make a boxplot and interpret the result.  
```{r}
ggplot(tidy_kudzu, aes(x = treatment, y = bone_mineral_density)) +
  geom_boxplot()
```
Notice that the high_dose treatment group has different spread.  
The control group seems to be skewed to the right.  
Generally, the high_dose treatment group has higher median compared to the rest of the groups.  
Based on this boxplot, the decision is this.  
The statistician on this study should **not** consider using an ordinary variance test for various reasons.  
The distribution is believed to be not normal, have unequal spreads, and the sample sizes are small for each treatment groups to apply the Central Limit Theorem.  
\

**Additional Graphs**

We can look at more graphs for more solid answer.  
```{r}
ggplot(tidy_kudzu, aes(sample = bone_mineral_density)) + 
  stat_qq() + stat_qq_line()
```
Notice that both low points and high points are too high.  
This indicates that the distribution is skewed to the right.  
Hence, it indicates that ordinary variance test could be problematic.  
\

By facetting, we can observe that the control group is the issue.  
```{r}
ggplot(tidy_kudzu, aes(sample = bone_mineral_density)) + 
  stat_qq() + stat_qq_line() + facet_wrap(~ treatment)
```
\

**d) Which Analysis Then?**

Since there are three different sample groups, and the distribution is not normal enough, the Mood's Median test would be suitable for this study to compare whether there exists a difference in bone mineral density with different types of treatments.  
\
\

**Reference**

I have mainly used the 'help' tool within the RStudio program itself.  

1. Shork, J. (2020). "Convert Data Frame Column to Numeric in R (2 Examples) | Change Factor, Character & Integer". Retrieved March 11, 2021 from https://statisticsglobe.com/convert-data-frame-column-to-numeric-in-r

2. Wickham, H. (2016). "tidyr 0.5.0". Retrieved March 11, 2021 from https://blog.rstudio.com/2016/06/13/tidyr-0-5-0/